\documentclass[11pt]{article}

\renewcommand*\familydefault{\sfdefault}

\usepackage{wrapfig}

%% the natbib package works better than cite 
\usepackage[square,numbers,sort&compress]{natbib}

\usepackage{color}

\usepackage[small,bf,up]{caption}
\renewcommand{\captionfont}{\footnotesize}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{graphics,epsfig,graphicx,float,subfigure,color}
\usepackage{algorithm,algorithmic}
\usepackage{amsmath,amssymb,amsbsy,amsfonts,amsthm}

\usepackage{comment}
\usepackage{url}
\usepackage{boxedminipage}
\usepackage[sf,bf,small]{titlesec}


\titlelabel{\thetitle.\,\,\,}

\newcommand{\bit}{\begin{itemize}}
\newcommand{\eit}{\end{itemize}}

\newcommand{\zapspace}{\topsep=0pt\partopsep=0pt\itemsep=0pt\parskip=0pt}
\newcommand{\todo}[1]{\textcolor{red}{#1}}



\setlength{\emergencystretch}{20pt}

\usepackage{amsmath,amssymb,amsbsy,amsfonts,amsthm,mathrsfs}
\usepackage{fullpage,subfigure,graphicx,epsfig,url,color}
\usepackage[plainpages=false, colorlinks=true,
   citecolor=black, filecolor=black, linkcolor=black,
   urlcolor=blue]{hyperref}

%\include{ogmacros}

\newcommand{\bdm}{\begin{displaymath}}
\newcommand{\edm}{\end{displaymath}}

\newcommand{\ben}{\begin{enumerate}}
\newcommand{\een}{\end{enumerate}}

\newcommand{\p}{\partial}
\newcommand{\bs}{\boldsymbol}

\renewcommand{\matrix}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\K}{\ensuremath{\matrix{K}}}
\newcommand{\F}{\ensuremath{\matrix{F}}}




\begin{document}
\pagestyle{empty}

\begin{center}
\large \textsf{%%
Spring 2020:\\
Computational Methodsfor Imaging Science\\
ESE 5932 \\[1mm]
\textbf{Getting started with FEniCS}}
\end{center}

\section{FEniCS overview}

FEniCS is a powerful, open-source suite of tools for automated
solution of partial differential equations (PDEs) using finite element (FE) method.
Part of the power for FEniCS
is the ease with which one can create FE solvers by describing PDEs
using weak forms in nearly-mathematical notation. The FEniCS project
can be found at:
\url{http://fenicsproject.org/} and comes with an extensive documentation and examples.\\

\noindent FEniCS includes a number of powerful features that include:
\vspace{-0.1in}
\begin{itemize}
\zapspace
\item[-] Automated solution of variational problems;
\item[-] Automated error control and adaptivity;
\item[-] An extensive library of finite elements;
\item[-] High performance linear algebra through backends to such
  libraries as PETSc;
\item[-] Visualization via a simple interactive plotting function, as
  well as output in VTK format;
% for visualization in ParaView. 
\item[-] Python and C++ interfaces;
\item[-] Extensive documentation (see for instance:
  \url{https://fenicsproject.org/documentation/}).
\end{itemize}

\section{FEniCS resources}

The documentation for FEniCS is extensive. Resources include:

\bit 
 \item[-] {\bf The FEniCS Tutorial.} The book \emph{Solving PDEs in Python: The FEniCS Tutorial Volume I}
 is the is the perfect guide for new users. The tutorial explains fundamental concepts of the finite element method,
 FEniCS programming, and demonstrates how to quickly solve a number of PDEs.
 
 The PDF version of the book can be downloaded (legally and for free) from\\
 \url{https://fenicsproject.org/pub/tutorial/pdf/fenics-tutorial-vol1.pdf}.
 
 Python scripts for all the examples described in the tutorial can be found at\\
 \url{https://github.com/hplgit/fenics-tutorial/tree/master/pub/python/vol1}
 
 \item[-] {\bf FEniCS Demos.} These documented demonstration programs are
   a great way to learn the different features in FEniCS.  They come
   already packaged in FEniCS when you install it and are available on-line at:\\
{\small \url{https://fenicsproject.org/docs/dolfin/latest/python/demos.html} }.

\item[-] {\bf Programmer's References.} Some of the classes and
  functions in DOLFIN are more frequently used than others. The Python
  implementations are described in\\
{\small \url{https://fenicsproject.org/docs/dolfin/latest/python/api.html} }.


\item[-] {\bf Getting Help.} See: \url{https://fenicsproject.org/community/}

\eit
\newpage
Other resources, although a little outdated and not fully compatible
with the latest versions of FEniCS, include:

\bit
\item[-] {\bf The FEniCS Book:} All 732 pages of the FEniCS book ({\em
  Automated Solution of Differential Equations by the Finite Element
  Method}) can be downloaded (legally!) from here:\\
{\footnotesize \url{http://launchpad.net/fenics-book/trunk/final/+download/fenics-book-2011-10-27-final.pdf}}.\\
%
This is the comprehensive reference to FEniCS, along with many
examples of the applications of FEniCS to problems in science and
engineering. You will notice that the first chapter of the book is
just the FEniCS Tutorial (with some minor editorial differences).

\item[-] {\bf The FEniCS Manual.} This is a 200-page excerpt from the
  FEniCS Book, including the FEniCS Tutorial, an introduction to the
  finite element method, and documentation of DOLFIN and UFL:\\
%
{\small \url{http://launchpad.net/fenics-book/trunk/final/+download/fenics-manual-2011-10-31.pdf}}.\\
%
Since it's an excerpt from the FEniCS Book, you probably won't need
it. 


\eit


\end{document}

